---
title: "HospitalRankings"
author: "Michael Zelenetz, Xiojing Yang"
date: "April 20, 2016"
output: html_document
---

The purpose of this project is to examine the Hospital Consumer Assessment of Healthcare Providers and Systems (HCAHPS) and related medical metrics that capture patient's overall experience at a hospital. 

As part of the Affordable Care Act, the government issued the creation of a national, standardized, publicly reported survey of patients' perspectives of hospital care (i.e. the HCAHPS). The HCAHPS contains numerous qualitative measures of a patient's experience including cleanliness of the hospital, pain management, effective communication by doctors and nurses, etc. The most visible and highly focused of these metrics are the star ratings. HCAHPS Scores are based on surveys sent to patients by the Centers for Medicaid and Medicare (CMS). The highest rating a hospital can get is 5 stars and the lowest is 1 star. A random sampling of patients receive surveys from CMS. The survey questions are primarily centered around patient satisfaction and quality of service in the hospital. Most of the questions are about the patients expirience with his or her providers such as: how did your doctor communicate with you? Did the staff explain the medications you were given? Was your pain well managed?

Higher HCAHPS scores may be in indication that the staff communicates effectively and that patients go home with a better understand of how to take care of themselves.

Our project will create a predictive model of star ratings for NY hospitals. First, we will look at other metrics within HCAHPS that can be leveraged within our model. Then, we will explore other hospital/Medicare databases and see whether metrics such as cost, mortality rates, infection rates, readmission rates, and waiting times are also predictive of star ratings.

Load data from local file:
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(broom)
library(knitr)
library(caret)
#cost sets
paymentandvalue <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Payment_and_value_of_care_-_Hospital.csv") #national
inpatientcost <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Hospital_Inpatient_Cost_Transparency__Beginning_2009.csv") #NYS

#risk of badness sets
PCIbyhospital <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Cardiac_Surgery_and_Percutaneous_Coronary_Interventions_by_Hospital___Beginning_2008.csv") #NYS

complicationshospital <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Readmissions_Complications_and_Deaths_-_Hospital.csv") #national

#service
hcahps <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/hcahps.csv") #national
timely <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Timely_and_Effective_Care_-_Hospital.csv") #national

#readmisisons
readmission <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Hospital_Readmissions_Reduction_Program.csv") #national 

#infections
hospitalinfection <- read.csv("https://raw.githubusercontent.com/anniey/Hospital-Ranking-CS107/master/Raw%20Data/Hospital-Acquired_Infections__Beginning_2008.csv") #ny
```

##Wrangling
Limit Data Sets to NYS only:
```{r}
paymentandvalue <- paymentandvalue %>% filter(State=="NY")
complicationshospital <- complicationshospital %>% filter(State=="NY")
hcahps <- hcahps %>% filter(State=="NY")
timely <- timely %>% filter(State=="NY")
readmission <- readmission %>% filter(State=="NY")
```

Additional wrangling of factor to numeric
```{r}
complicationshospital$Denominator <- as.numeric(as.character(complicationshospital$Denominator))
complicationshospital$Score <- as.numeric(as.character(complicationshospital$Score))

inpatientcost$Mean.Charge <- sub('\\$','', as.character(levels(inpatientcost$Mean.Charge))[inpatientcost$Mean.Charge]) %>%
  as.numeric()

inpatientcost$Median.Charge <- sub('\\$','', as.character(levels(inpatientcost$Median.Charge))[inpatientcost$Median.Charge]) %>%
  as.numeric()

#change payment and denominator into numeric
paymentandvalue$Payment <- sub('\\$','', as.character(levels(paymentandvalue$Payment))[paymentandvalue$Payment]) %>%
  as.numeric()

paymentandvalue$Denominator <- sub('\\,','', as.character(levels(paymentandvalue$Denominator))[paymentandvalue$Denominator]) %>%
  as.numeric()
```



#Part 1: Examinig HCAHPS

```{r}
#spread the ratings and the other scores
HCAHPS <- hcahps %>%
  select(Provider.ID, HCAHPS.Measure.ID, Patient.Survey.Star.Rating) %>%
  filter(HCAHPS.Measure.ID == "H_STAR_RATING") %>%
  spread(HCAHPS.Measure.ID, Patient.Survey.Star.Rating)

#only keep the aggregate metrics
HCAHPS <- hcahps %>%
  select(Provider.ID, HCAHPS.Measure.ID, HCAHPS.Linear.Mean.Value) %>%
  filter(HCAHPS.Measure.ID %in% c("H_CLEAN_LINEAR_SCORE", "H_COMP_1_LINEAR_SCORE", "H_COMP_2_LINEAR_SCORE","H_COMP_3_LINEAR_SCORE", "H_COMP_4_LINEAR_SCORE","H_COMP_5_LINEAR_SCORE", "H_COMP_6_LINEAR_SCORE","H_COMP_7_LINEAR_SCORE","H_HSP_RATING_LINEAR_SCORE", "H_QUIET_LINEAR_SCORE")) %>%
  right_join(HCAHPS, by = "Provider.ID")

#clean NAs
HCAHPS[HCAHPS == "Not Available"] = NA
HCAHPS <- na.omit(HCAHPS)

#transform classes
HCAHPS$HCAHPS.Linear.Mean.Value <- as.numeric(as.character(HCAHPS$HCAHPS.Linear.Mean.Value))

#refactor star rating to account for removed factors
HCAHPS$H_STAR_RATING <- factor(HCAHPS$H_STAR_RATING)

```

Let's plot these scores and see if there is any relationship to star rating.

```{r}
HCAHPS %>%
  ggplot(aes(H_STAR_RATING, HCAHPS.Linear.Mean.Value)) +
  geom_boxplot()

```

A quick look at the aggregated scores against star ratings boxplot shows a weak positive relationship between the scores and the star rating. Now, let's see which of the scores are most predictive of a hospitals star rating.

```{r}
#find the distance between the scores and star rating
HCAHPS <- HCAHPS %>%
  spread(HCAHPS.Measure.ID, HCAHPS.Linear.Mean.Value) 

HCAHPS_sum <- HCAHPS %>%
  select(-c(Provider.ID))

#let's make the column names friendly
colnames(HCAHPS_sum) <- c("Star Rating", "Cleanliness", "Nurse Comm.", "Doctor Comm.", "Staff Responsiveness", "Pain Mmgt.", "Medication Comm.", "Discharge Information", "Care Transition", "Overall Rating", "Quietness")

HCAHPS_dist <- as.matrix(HCAHPS_sum) %>%
  t() %>%
  dist()

heatmap(as.matrix(HCAHPS_dist), margins = c(10,10))
```

It looks like communication about medicine is the closest to star rating, followed by quietness.

Now, let's see if we can build a knn model from these additional HCAHPS metrics. First, we will need to determine the best K to use.

```{r}
#let's find the best k
set.seed(1)
control <- trainControl(method='cv', number=10, p=.8)
res_knn <- train(H_STAR_RATING ~ .,
             data = HCAHPS_sum,
             method = "knn",
             trControl = control,
             tuneLength = 1,
             tuneGrid=data.frame(k=seq(1,15,1)),
             metric="Accuracy")

res_knn$results %>% 
  ggplot(aes(k, Accuracy, ymin= Accuracy - AccuracySD, 
             ymax = Accuracy + AccuracySD)) +
  geom_point() + geom_errorbar()
```

From the above accuracy graph, it looks like a k of 9 will give us the best ratings.

```{r}
#let's create a model with k = 9
inTrain <- createDataPartition(y = HCAHPS_sum$H_STAR_RATING, p = 0.8)
train_set <- slice(HCAHPS_sum, inTrain$Resample1)
test_set <- slice(HCAHPS_sum, -inTrain$Resample1)

#reset factors for test set
test_set$H_STAR_RATING <- factor(test_set$H_STAR_RATING)

#fit the data
fit <- knn3(H_STAR_RATING~., data = train_set, k=9)
f_hat <- predict(fit, newdata = test_set)
f_hat_max <- apply(f_hat,1,max)
pred <- apply(f_hat,1,which.max)
tab <- table(pred = round(pred), truth = test_set$H_STAR_RATING)

confusionMatrix(tab)$overall["Accuracy"]
  
```

From the above, we see that the remaining metrics in HCAHPS has about a 86% accuracy rating in predicting star ratings.

Now, we will expand our search outside of the HCAHPS and see if metrics from other databases can help us improve our predicitons. Before we link these new metrics to HCAHPS, we will first explore each dataset and examine some additional hypothesis that would impact patient experience.

#Data Exploration of other potential predictors

As we have several other potential predictors in our other datasets, we will limit this preliminary data exploration to just those that have cost and mortality metrics. 

##Cost

One clear potential predictor in a patient's experience is the cost of treatment.

First, let us sanity check this dataset and verify that cost is higher for more severe treatments.

```{r}
Severity<- inpatientcost %>% 
  filter(APR.DRG.Description=="Heart Failure")

#boxplot of charge by severity
Severity %>%
  ggplot(aes(APR.Severity.of.Illness.Description, Mean.Charge)) +
  geom_boxplot()

```

As expected, it appears extreme cases have higher charges than the other cases. That being said, interestingly enough, there is not much difference in cost between major and minor treatments.

Let's see if there is a relationship between dischage and mean cost in this dataset. The idea behind this hypothesis is that hospitals that treat more patients for a certain procedure or disorder may have improved efficiencies that allows hospitals to lower the treatmet charge. 

```{r}

#boxplot of charge by severity
Severity %>%
  ggplot(aes(Discharges, Mean.Charge)) +
  geom_point() +
  facet_wrap(~APR.Severity.of.Illness.Description, scales = "free_x")

```

Unfortunately, it looks like there is no relationship between number of patients seen and cost of treatment. This suggests that, contrary to expectation, hospitals that see more cases of a certain disorder/disease may not actually have an advantage in scalibility to reduce costs.


##Mortality

The next potential predictor we will examine is mortality.

We will re-examine our earlier test of the relationship between cost and number of patients seen.

```{r}

#clean the data
PV <- paymentandvalue %>%
  select(Provider.ID, Denominator, Payment, Payment.measure.ID, Value.of.care.category) %>%
  na.omit() %>%
  filter(Denominator != "Not Available")

#plot cost and number of cases a hospital sees
ggplot(PV, aes(Denominator, Payment)) + 
  geom_point() +
  facet_wrap(~Payment.measure.ID, scales = "free_x") +
  xlab("Case count")

```

Again, we see that there is not really a change in cost for a treatment with increased number of cases seen.

Let's now see whether value of care, as defined by mortality and payment intersection, is impacted by the number of cases seen.

```{r}
#let's now check number of cases and value of care
PV %>%
  ggplot(aes(Value.of.care.category, Denominator)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Number of Cases")

#let's check heart disease in particular
PV %>% filter(Payment.measure.ID == "PAYM_30_HF") %>%
  ggplot(aes(Value.of.care.category, Denominator)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Number of Cases")


```

From the boxplots, we can see that number of cases seen does not appear to vary much between average mortality and worse mortality outcomes. However, it does appear that hospitals with better mortality tend to have seen more cases.

Let's focus on just mortality, ignoring the payment dimension, and observe the impact of cases there.

```{r}
#bucket the mortality rates, ignoring payment
PV <- PV %>%
  mutate(Care.Cat = ifelse(grepl("Better mortality", Value.of.care.category), "Better Mortality", 
                           ifelse(grepl("Average mortality", Value.of.care.category), "Average Mortality", "Worse mortality")))

#let's plot a boxplot of the number of cases by group
PV %>%
  ggplot(aes(Care.Cat, Denominator)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Number of Cases") +
  facet_wrap(~Payment.measure.ID, scales = "free_x")

```

In ignoring the payment categories and focusing on just mortality, we can see that mortality does seem to be better at hospitals that observe more cases for all three types of illnesses. Let us see if there is enough of a relationship for us to predict mortality rates using number of cases seen by a hospital. We will focus on heart failure.

```{r}
set.seed(1)
#turn character into numeric
PV_HF <- mutate(PV, Care.Cat = ifelse(grepl("Better mortality", Value.of.care.category), 3, 
                           ifelse(grepl("Average mortality", Value.of.care.category), 2, 1))) %>%
  filter(Payment.measure.ID == "PAYM_30_HF")


#create train and test sets
inTrain <- createDataPartition(y = PV_HF$Care.Cat, p = 0.8)
train_set <- slice(PV_HF, inTrain$Resample1)
test_set <- slice(PV_HF, -inTrain$Resample1)

#fit the data
fit <- glm(Care.Cat ~ Denominator, data=train_set)
pred <- predict(fit, newdata = test_set, type = "response")
tab <- table(pred = round(pred), truth = test_set$Care.Cat)

confusionMatrix(tab)$overall["Accuracy"]

```

It looks like just using the number of cases is actually fairly predictive of the mortality rates for heart failure at hospitals. Let's see if we can replicate this with a more common disorder like pneumonia:

```{r}
set.seed(1)
#turn character into numeric
PV_PN <- mutate(PV, Care.Cat = ifelse(grepl("Better mortality", Value.of.care.category), 3, 
                           ifelse(grepl("Average mortality", Value.of.care.category), 2, 1))) %>%
  filter(Payment.measure.ID == "PAYM_30_PN")


#create train and test sets
inTrain <- createDataPartition(y = PV_PN$Care.Cat, p = 0.8)
train_set <- slice(PV_PN, inTrain$Resample1)
test_set <- slice(PV_PN, -inTrain$Resample1)

#fit the data
fit <- glm(Care.Cat ~ Denominator, data=train_set)
pred <- predict(fit, newdata = test_set, type = "response")
tab <- table(pred = round(pred), truth = test_set$Care.Cat)

tab

```

From the above, we can see that number of cases seen does not have a strong predictive capability for mortality rates for pneumonia. So, the effect we observed for heart failure may just be limited to more complex diseases or diseases that may require more surgical intervention.

Let's see what happens when we leverage another database that has actual mortality rates. We will focus on heart failure for now.

```{r}
CH <- complicationshospital %>%
  select(Measure.ID, Denominator, Score)

#let's look at the relationship for HF only
CH %>%
  filter(Measure.ID == "MORT_30_HF") %>%
  ggplot(aes(Denominator, Score)) +
  geom_point() +
  geom_smooth()
```

It looks like there is a slight increase in mortality rate when the number of cases increase, but then it drops off as the number of cases continue to grow. Let's now explore additional measures such as mortality rate for AMI and Strokes.

```{r}
#let's look at the relationship for AMI and STK
CH %>%
  filter(Measure.ID %in% c("MORT_30_HF", "MORT_30_AMI", "MORT_30_STK")) %>%
  ggplot(aes(Denominator, Score, colour = Measure.ID)) +
  geom_point() +
  geom_smooth() 

```

The drop in mortality rate is even more pronounced for AMI.

Let's see what happens when we try to fit a regression to number of cases and mortality rate of AMI and HF.

```{r}

CH_HF <- CH %>%
  filter(Measure.ID == "MORT_30_HF") %>%
  na.omit()
  
CH_AMI <- CH %>%
  filter(Measure.ID == "MORT_30_AMI") %>%
  na.omit()

res_HF <- CH %>%
  filter(Measure.ID %in% c("MORT_30_HF")) %>%
  lm(Score ~ Denominator, data = .) %>%
  tidy(conf.int = TRUE)

res_AMI <- CH %>%
  filter(Measure.ID %in% c("MORT_30_AMI")) %>%
  lm(Score ~ Denominator, data = .) %>%
  tidy(conf.int = TRUE)

kable(res_HF)
kable(res_AMI)
```

From the above, we can see that with each additional case of HF, a hospital's rate of mortality decreases between 0.01% to 0.02%. For AMI, the rate of decrease is even higher at 0.01% to 0.04%. 

Another database that has mortality rating is PCIbyhospital. Let's see if we can find the same relationship there.

```{r}

#removing observed mortality rate of 0
PCI_mort <- PCIbyhospital %>%
  filter(Procedure == "All PCI", Hospital.Name != "NYS - All Hospitals", Observed.Mortality.Rate >0) %>%
  select(Number.of.Cases, Observed.Mortality.Rate, Risk.Adjusted.Mortality.Rate)

#plot Risk Adjusted rates
PCI_mort %>%
  ggplot(aes(Number.of.Cases, Risk.Adjusted.Mortality.Rate)) +
  geom_point() +
  geom_smooth()

#plot observed rate
PCI_mort %>%
  ggplot(aes(Number.of.Cases, Observed.Mortality.Rate)) +
  geom_point() +
  geom_smooth()

```

We see a fairly sharp drop in mortality rate that plateaus once the number of cases surpasses 500. This appears to apply to both the observed and risk adjusted mortality rate. Let's now fit a regression to number of cases against the two rates.

```{r}

res_Obs <- PCI_mort %>%
  lm(Risk.Adjusted.Mortality.Rate ~ Number.of.Cases, data = .) %>%
  tidy(conf.int = TRUE)

res_Adj <- PCI_mort %>%
  lm(Observed.Mortality.Rate ~ Number.of.Cases, data = .) %>%
  tidy(conf.int = TRUE)

kable(res_Obs)
kable(res_Adj)
```

We see about the same relationship of 0.01%-0.04% decrease in mortality rate for each additional case seen.

#Final Model for HCAHPS Star Rating

Now that we have explored the other datasets. Let's add the additional metrics to the HCAHPS dataset and see if we can improve our model.

First, we will examine cost.

```{r}
#add cost metrics
providerID_data <- paymentandvalue %>%
  select(c(Provider.ID, Hospital.name, Payment.measure.ID, Denominator, Payment)) %>%
  right_join(providerID_data, by = "Provider.ID")

providerID_data %>% 
  filter(Payment.measure.ID == "PAYM_30_AMI") %>%
  ggplot(aes(H_STAR_RATING, Payment)) +
  geom_boxplot() +
  ggtitle("Payment for AMI vs. Star Rating")

providerID_data %>% 
  filter(Payment.measure.ID == "PAYM_30_HF") %>%
  ggplot(aes(H_STAR_RATING, Payment)) +
  geom_boxplot() +
  ggtitle("Payment for Heart Failure vs Star Rating")

providerID_data %>% 
  filter(Payment.measure.ID == "PAYM_30_PN") %>%
  ggplot(aes(H_STAR_RATING, Payment)) +
  geom_boxplot() +
  ggtitle("Payment for Pneumonia vs Star Rating")


```

Interestingly, much like mortality, cost does not appear to have a consistent relationship with star rating. Only cost for pneumonia treatment appears to be decreasing with increase star rating.

What about mortality rates?

```{r}

#select the columns we want relating to mortality
providerID_data <- complicationshospital %>%
  select(c(Provider.ID, Hospital.Name, Measure.ID, Score)) %>%
  spread(Measure.ID, Score)

providerID_data[providerID_data == "Not Available"] = NA

#join with our HCAHPS dataset   
providerID_data <- HCAHPS %>%
  transform(Provider.ID = factor(Provider.ID)) %>%
  right_join(providerID_data, by = "Provider.ID")

#plot our results
providerID_data %>% 
  select(H_STAR_RATING, MORT_30_AMI) %>%
  unique() %>%
  ggplot(aes(H_STAR_RATING, MORT_30_AMI)) +
  geom_boxplot() +
  ggtitle("AMI Mortality vs Star Rating")

providerID_data %>% 
  select(H_STAR_RATING, MORT_30_HF) %>%
  ggplot(aes(H_STAR_RATING, MORT_30_HF)) +
  geom_boxplot() +
  ggtitle("Heart Failure Mortality vs Star Rating")

providerID_data %>% 
  select(H_STAR_RATING, MORT_30_STK) %>%
  ggplot(aes(H_STAR_RATING, MORT_30_STK)) +
  geom_boxplot() +
  ggtitle("Stroke Mortality vs Star Rating")

providerID_data %>% 
  select(H_STAR_RATING, MORT_30_PN) %>%
  ggplot(aes(H_STAR_RATING, MORT_30_PN)) +
  geom_boxplot() +
  ggtitle("Pneumonia Mortatlity vs Star Rating")
```

Much like cost, mortality does not appear to have a consistent relationship with star rating. It looks like there is no consistent relationship between mortality and star ratings. AMI mortality rates only had a slight decline with increased star rating. Surprisingly, HF mortality rates appear to actually increase with higher star ratings.


We will now have to check the other datababse with mortality ratings. In order to do that though, we must first find a way to join our national datasets, which uses provider ID, with our PCIbyhospital NY dataset, which uses facility ID. There are no common code between the two, so we will have to perform our join using hospital names.


```{r}

#use hospital infection naming convention as that is the closest to the provider naming convention
facilityID_data <- hospitalinfection %>%
  filter(Facility.Id > 0, Year == 2014 ) %>%
  select(Facility.Id, Hospital.Name, Infections.observed) %>%
  group_by(Facility.Id, Hospital.Name) %>%
  summarise(Infections = sum(Infections.observed) )

#adjust col names of PCI
colnames(PCIbyhospital)[1] <- "Facility.Id"
colnames(PCIbyhospital)[6] <- "Year"

#only take risk adjusted mortality rate and the latest year
facilityID_data <- PCIbyhospital %>%
  filter(Year == 2011, Procedure == "All PCI") %>%
  select(c(Facility.Id, Number.of.Cases, Risk.Adjusted.Mortality.Rate)) %>%
  right_join(facilityID_data, by = "Facility.Id")


#clean case convention and column name
facilityID_data$Hospital.Name <- toupper(facilityID_data$Hospital.Name)

```


Now let's try to join the ProviderID dataset with the FacilityID dataset using the Hospital/Facility Name. First, we need to clean up some of the varying naming conventions between the two datasets. We will use ProviderID as the convention given that is the one used by HCAHPS

```{r}
#find the hospital names that are slightly different between the datasets

facilityID_data$Hospital.Name <- as.character(facilityID_data$Hospital.Name)
providerID_data$Hospital.Name <- as.character(providerID_data$Hospital.Name)

FacilityNames <- facilityID_data %>%
  select(Hospital.Name) %>%
  mutate(Origin = "Facility") %>%
  as.data.frame() %>%
  unique()

HospitalNames <- providerID_data %>%
  select(Hospital.Name) %>%
  mutate(Origin = "Provider") %>%
  as.data.frame() %>%
  unique()

#merge the tables and find where there is unmerged rows
ProblemNames <- merge(FacilityNames, HospitalNames, by = "Hospital.Name", all = TRUE)

```


Quickly scanning the list of merged names, we notice that a common difference in convention between the datasets is the use of "INC" vs ", INC". Let's update FacilityID from "INC" to ", INC".
```{r}

#Update FacilityID's uses "INC" to match ProviderID's ", INC"
facilityID_data$Hospital.Name <- gsub(" INC", ", INC", facilityID_data$Hospital.Name)

#rerun the merged datasets
FacilityNames <- facilityID_data %>%
  select(Hospital.Name) %>%
  as.data.frame() %>%
  unique()

ProblemNames <- merge(FacilityNames, HospitalNames, by = "Hospital.Name", all = TRUE)
```

It also looks like the facility database has separate IDs for different divisions of a hospital provider. Let's remap all these divisions to the parent provider
```{r}

#rename Catskill to remove from further cleaning as we don't want to remove the - in this case
facilityID_data$Hospital.Name <- gsub("CATSKILL REGIONAL MEDICAL CENTER - G. HERMANN SITE", "CATSKILL REGIONAL MEDICAL CENTER G HERMANN SITE", facilityID_data$Hospital.Name)

#remove division name following -
facilityID_data$Hospital.Name <- gsub(" - [A-z ]*", "", facilityID_data$Hospital.Name)

#rerun the merged datasets
FacilityNames <- facilityID_data %>%
  select(Hospital.Name) %>%
  as.data.frame() %>%
  unique()

ProblemNames <- merge(FacilityNames, HospitalNames, by = "Hospital.Name", all = TRUE)
```

We still have a couple more manual changes to make

```{r}

#create table remapping facility name to hospital name
facility_orig = c("ADIRONDACK MEDICAL CENTER-SARANAC LAKE SITE", "BROOKHAVEN MEMORIAL HOSPITAL MEDICAL CENTER INC", "BROOKLYN HOSPITAL CENTER AT DOWNTOWN CAMPUS", "CATSKILL REGIONAL MEDICAL CENTER - G. HERMANN SITE", "CHAMPLAIN VALLEY PHYSICIANS HOSPITAL MEDICAL CENTER", "CLIFTON-FINE HOSPITAL", "FAXTON-ST LUKES HEALTHCARE ST LUKES DIVISION", "FAXTON-ST LUKES HEALTHCARE FAXTON DIVISION", "JOHN T MATHER MEMORIAL HOSPITAL OF PORT JEFFERSON NEW YORK, INC", "MARGARETVILLE HOSPITAL", "MONTEFIORE", "MONTEFIORE MED CENTER", "MONTEFIORE MEDICAL CENTER& LUCY MOSES DIV", "MOUNT VERNON HOSPITAL", "MOUNT ST MARYS HOSPITAL AND HEALTH CENTER", "NEW YORK COMMUNITY HOSPITAL OF BROOKLYN,, INC", "NEW YORK PRESBYTERIAN HOSPITAL", "RIVER HOSPITAL,, INC.", "ROME MEMORIAL HOSPITAL,, INC", "SCHUYLER HOSPITAL", "SOLDIERS AND SAILORS MEMORIAL HOSPITAL OF YATES, INC", "ST JOHNS EPISCOPAL HOSPITAL SO SHORE", "ST JOSEPHS HOSPITAL", "ST JOSEPHS HOSPITAL HEALTH CENTER", "ST JOSEPH'S MC-ST VINCENTS WESTCHESTER DIVISION", "ST LUKE'S CORNWALL HOSPITAL/NEWBURGH", "ST LUKES ROOSEVELT HOSPITAL", "ST LUKES ROOSEVELT HOSPITAL CENTER", "ST PETERS HOSPITAL", "ST. JOSEPH HOSPITAL", "STATEN ISLAND UNIVERSITY HOSP-NORTH", "STATEN ISLAND UNIVERSITY HOSP-SOUTH", "UNITED HEALTH SERVICES HOSPITALS, INC.", "UNITED MEMORIAL MEDICAL CENTER BANK STREET CAMPUS", "UNITED MEMORIAL MEDICAL CENTER NORTH STREET CAMPUS", "UNIVERSITY HOSPITAL", "UNIVERSITY HOSPITAL OF BROOKLYN", "UNIVERSITY HOSPITAL SUNY HEALTH SCIENCE CENTER", "WOMANS CHRISTIAN ASSOC HOSPITAL", "WOODHULL MEDICAL & MENTAL HEALTH CENTER")

facility_new = c("ADIRONDACK MEDICAL CENTER", "BROOKHAVEN MEMORIAL HOSPITAL MEDICAL CENTER", "BROOKLYN HOSPITAL CENTER", "CATSKILL REGIONAL MEDICAL CENTER - G HERMANN SITE", "CHAMPLAIN VALLEY PHYSICIANS HOSPITAL MEDICAL CTR", "CLIFTON FINE HOSPITAL", "FAXTON-ST LUKE'S HEALTHCARE", "FAXTON-ST LUKE'S HEALTHCARE", "JOHN T MATHER MEMORIAL HOSPITAL OF PORT JEFFERSON", "MARGARETVILLE MEMORIAL HOSPITAL", "MONTEFIORE MEDICAL CENTER", "MONTEFIORE MEDICAL CENTER", "MONTEFIORE MEDICAL CENTER", "MONTEFIORE MOUNT VERNON HOSPITAL", "MOUNT ST MARY'S HOSPITAL AND HEALTH CENTER", "NEW YORK COMMUNITY HOSPITAL OF BROOKLYN, INC.", "NEW YORK-PRESBYTERIAN HOSPITAL", "RIVER HOSPITAL, INC", "ROME MEMORIAL HOSPITAL, INC", "SCHUYLER HOSPITAL, INC", "SOLDIERS AND SAILORS MEMORIAL HOSPITAL OF YATES", "ST JOHN'S EPISCOPAL HOSPITAL AT SOUTH SHORE", "ST JOSEPH'S HOSPITAL, INC", "ST JOSEPH'S HOSPITAL HEALTH CENTER", "ST JOSEPH'S MEDICAL CENTER", "ST LUKE'S CORNWALL HOSPITAL", "ST LUKE'S ROOSEVELT HOSPITAL","ST LUKE'S ROOSEVELT HOSPITAL CENTER", "ST PETER'S HOSPITAL", "ST JOSEPH HOSPITAL", "STATEN ISLAND UNIVERSITY HOSPITAL", "STATEN ISLAND UNIVERSITY HOSPITAL", "UNITED HEALTH SERVICES HOSPITALS, INC", "UNITED MEMORIAL MEDICAL CENTER", "UNITED MEMORIAL MEDICAL CENTER", "UNIVERSITY HOSPITAL (STONY BROOK)", "UNIVERSITY HOSPITAL OF BROOKLYN (DOWNSTATE)", "UNIVERSITY HOSPITAL S U N Y HEALTH SCIENCE CENTER", "WOMAN'S CHRISTIAN ASSOCIATION HOSPITAL", "WOODHULL MEDICAL AND MENTAL HEALTH CENTER")

#renaming table
remapped_names <- data.frame("Facility Name" = facility_orig, "Provider Name" = facility_new, stringsAsFactors = FALSE)

#rename the hospitals in the facilityID_data
facilityID_data$Hospital.Name <- sapply(facilityID_data$Hospital.Name, function(x){
  ifelse(x %in% remapped_names$Facility.Name, remapped_names[facility_orig == x, 2], x)
})

```

Let us return to our analysis of mortality rates. We will examine whether the risk adjusted mortality rates at hospitals are predictive of star ratings

```{r}
#merge mortality info
combined_data <- facilityID_data %>% 
  select(Hospital.Name, Number.of.Cases, Risk.Adjusted.Mortality.Rate) %>%
  right_join(providerID_data, by = "Hospital.Name")

combined_data %>%
  ggplot(aes(H_STAR_RATING, Risk.Adjusted.Mortality.Rate)) +
  geom_boxplot() +
  ggtitle("Risk Adjusted Mortality vs. Star Rating")

```

Based on the above boxplots, it looks like there is no real difference in mortality rate between the star ratings, though there is actually a slight increase in the rate for 4 star hospitals. This is similar to our earlier finding on heart failures.

Finally, to round out our examination of various survival metrics, let us also examine infections.

```{r}
#merge infection info
combined_data <- facilityID_data %>% 
  select(Hospital.Name, Infections) %>%
  right_join(providerID_data, by = "Hospital.Name")

combined_data %>%
  ggplot(aes(H_STAR_RATING, Infections)) +
  geom_boxplot() +
  ggtitle("Total Hospital Infections vs. Star Rating")

```

It looks like infections from hospitals is slightly lower for the higher 4 star hospitals, but not significantly different for the other hospitals.


Time spent in the emergency department is more commonly being looked at as an indicator of the overall patient expirience. We looked at the time it took hospitals to move admitted patients out of the ED to their rooms and compared it with HCAHPS score.
```{r}
#time in ED
temp <- timely %>%
  filter(Measure.ID=="ED_1b") #Median time from emergency department arrival to emergency department departure for admitted emergency department patients

temp <- left_join(temp, readmissionInfection, by= "Hospital.Name") %>%
  select(Hospital.Name, Measure.ID, Score, Sample, readmissionRate)
ggplot(temp, aes(x=temp$readmissionRate, y= temp$Score)) + geom_point() + xlab("Readmission Rate") + ylab("ED Wait Times (for admitted patients)")

temp <- left_join(temp, hcahpsSummary, by="Hospital.Name")
temp$Score <- gsub("Not Available", NA, temp$Score)
temp$Score <- as.numeric(as.character(temp$Score))

temp %>%
  na.omit() %>%
  ggplot(aes(Patient.Survey.Star.Rating, Score)) + geom_boxplot() + xlab("HCAHPS Score") + ylab("ED Wait Time")
``` 

It appears that as the hospitals with lower HCAHPS scores tended to have higher ED wait times. 


#Readmission VS HCAHPS
 We hypothesized that hospitals with higher HCAHPS scores would have lower 30 day readmission rates. 

We analyzed the rate of patients readmitted for a complaint related to their original admission within 30 days of discharge for patients of all disease types:
```{r}
readmissionInfection <- filter(readmission, Measure.Name=="READM-30-COPD-HRRP") %>% 
  select(Hospital.Name, Provider.Number, Number.of.Readmissions, Number.of.Discharges)

#convert to correct type
readmissionInfection[, 3] <- as.numeric(as.character( readmissionInfection[, 3] ))
readmissionInfection[, 4] <- as.numeric(as.character( readmissionInfection[, 4] ))
readmissionInfection <- na.omit(readmissionInfection)

readmissionInfection <- mutate(readmissionInfection, readmissionRate= Number.of.Readmissions/Number.of.Discharges)

readmitHCAHPS <- left_join(hcahpsSummary, readmissionInfection, by="Hospital.Name")
#filter by overall score
readmitHCAHPS %>%
  filter(HCAHPS.Question=="Summary star rating")%>%
  ggplot(aes(Patient.Survey.Star.Rating, readmissionRate)) + geom_boxplot() + xlab("HCAHPS Score") + ylab("Readmission Rate")
```

Indeed, there seems to be a trend towards lower 30 readmission rates for hospitals with higher HCAHPS scores. 

If our theory is, indeed, true then we would expect that patients with lower readmission rates would rate their discharge instructions and communication about medicines highly:
```{r}
readmitHCAHPS %>%
  filter(HCAHPS.Question=="Discharge information - star rating") %>%
  ggplot(aes(Patient.Survey.Star.Rating, readmissionRate)) + geom_boxplot() + xlab("Discharge Instructions Score") + ylab("Readmission Rate")+ ggtitle("Discharge Information")

readmitHCAHPS %>%
  filter(HCAHPS.Question=="Communication about medicines - star rating") %>%
  ggplot(aes(Patient.Survey.Star.Rating, readmissionRate)) + geom_boxplot() + xlab("Communication about Medicine Score") + ylab("Readmission Rate") + ggtitle("Communication about Medicine")

```
There seems to be a downward trend in readmssion rates as the rating of the discharge instructions and medication communication increase.


Look at some serious complications complications:
```{r}
HFcompScore <- temp %>% filter(Measure.Name=="Heart failure (HF) 30-Day Readmission Rate", rm.na=TRUE) %>% na.omit()
HFcompScore <- as.data.frame(HFcompScore)

HFcompScore <- HFcompScore[order(HFcompScore$Score),]

BloodClotScore <- temp %>% filter(Measure.Name=="Serious blood clots after surgery", rm.na=TRUE) %>% na.omit()
BloodClotScore$Score <- as.numeric(BloodClotScore$Score)
BloodClotScore <- BloodClotScore[order(BloodClotScore$Score),]

names(HFcompScore)[2] <- "HF.Score"
names(BloodClotScore)[2] <- "Clot.Score"

CompsHCAHPS <- left_join(HFcompScore, BloodClotScore, by= "Hospital.Name") %>%
  select(Hospital.Name, HF.Score, Clot.Score)
CompsHCAHPS <- left_join(CompsHCAHPS, hcahpsRating, by= "Hospital.Name")
CompsHCAHPS <- na.omit(CompsHCAHPS)

CompsHCAHPS %>%
  ggplot(aes(Summary.Rating, Clot.Score)) + geom_boxplot() + xlab("HCAHPS Score") + ylab("Clot Rate") + ggtitle("Clots")
```

There is no effect of serious side effects--in the example: blood clots--on HCAHPS Scores. It doesn't seem that people are likely to change their evaluation of the care based on complications.

##Aggregating the findings

From all of the analysis above, 

```{r}

```